Towards a Machine Learning approach for Aggregate Computing

### 2021-11-07 paper-2021-woa-ac-ml.tex
put intro changes made by metaphori

\section{Introduction}
Nowadays, computer engineers have to deal with Collective Adaptive Systems (CASs)
 due to the increasing interconnected computational devices placed in ever-changing environments.
 Examples of those include robot swarms, smart cities and augmented crowds with smart devices.

CAS are notoriously hard~\cite{DBLP:conf/huc/Ferscha15} to design as they are characterised by 
\begin{itemize}
\item a global order that emerges from local node interactions, 
\item decentralised control, and 
\item adaptive behaviours towards environmental changes to pursuit a collective goal.
\end{itemize} 
%
So, over the years, in literature, various approaches have tried to handle this complexity. 
%
Some of them take inspiration from the natural system
 composed of social animals --- like bees, fish, and ants. 
%
Here, a sort of hive mind arises -- 
 also referred to as swarm intelligence --  
 born from local interactions between agents. 
%
These kinds of behaviours are accomplished with self-organisation, 
 namely a global order that emerges from continuous 
 interactions between simple entities.

>>>>

\section{Introduction}
Recent trends like pervasive and autonomic computing 
 promote a vision of artificially designed Collective Adaptive Systems (CASs),
 namely collections of agents coordinating and adapting %as wholes 
 to pursue joint goals in changing environments.
% due to the increasing interconnected computational devices placed in ever-changing environments.
 Examples of CASs include robot swarms, smart cities, and digitally-augmented crowds.
%
%CASs are characterised by 
%\begin{itemize}
%\item a global order that emerges from local node interactions, 
%\item  decentralised control, and 
%\item adaptive behaviours towards environmental changes to pursuit a collective goal.
%\end{itemize}
%
CAS are notoriously hard to design and control 
 %due to as part of complex systems
 as globally desired behaviour
 has to emerge from local behaviours and interactions. 
So, over the years, in literature, various approaches have tried to handle this complexity. 
%
Some of them take inspiration from the natural system
 composed of social animals --- like bees, fish, and ants. 
%
Here, a sort of hive mind arises -- 
 also referred to as swarm intelligence --  
 born from local interactions between agents. 
%
These kinds of behaviours are accomplished with self-organisation, 
 namely a global order that emerges from continuous 
 interactions between simple entities.
